{\bf A Review on Recent Advances in Unsupervised Relation Extraction} \\ \it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal

### 2013-07-21 term-paper/paper.tex
Added: pictures DIRT finished

\usepackage{graphics}
\usepackage{epsfig}
\usepackage{times}
\usepackage{amsmath}
\usepackage{framed, color}
\usepackage{fancybox}
\definecolor{shadecolor}{rgb}{0.8,0.8,0.8}

@@

The aim of this paper is to review recent and influential methods on
Unsupervised Relation Extraction. In the first chapter, the definition and a general background
for relation extraction task is provided which identifies important aspects and
difficulties of the task. In the second chapter, five major previous works are
briefly reviewed. The third chapter is dedicated to a weakly supervised method, distant supervision, which is 
necessary due to its impact on recent advances in the task. And
finally in the last chapter, the paper will be concluded by comparison of discussed methods and important lessons learned from each of them.

@@

\subsection{Inference Selectional Preferences}
\label{ch:model}

@@

In order to model this type of constraint on discovery of paraphrases, Pantel et al. have proposed that
relations which are similar but are not sharing a same class of arguments should be filtered out. For each relation, 
they compute a distribution of possible semantic classes for its arguments. For two equivalent relations, they will be kept
if this distribution is similar for both.

@@

\textbf{Rel-LDA} is the first model proposed in (?? Yao). 
In this model, features, $f$, are generated from a distribution , $\Phi_{rf}$. Each type
 of relation is represented with a binary indicator variable, $r$. Each document is a mixture of few relations
  and relations are generated from a multinomial distribution $\Theta_{doc}$. $\Theta_{doc}$ is a distribution
  of relations for a specific document and can be shown as $P(r|doc)$. By choosing a right prior distribution for $\Theta$
   and $\Phi$ we can impose an assumption that any document contains a few number of relation types. 
   Another advantage of having prior is that it helps to avoid overfitting. Dirichlet prior with small parameter $\alpha$ is 
   chosen for this purpose in the paper. For more on the role of priors and specially Dirichlet prior
    please read ?? and ??.
    Rel-LDA is decribed with a graphical model in figure ???.
    Shaded circles are showing the observable variables and other circles are hidden variables except 
    the priors which are set by ourselves. The direction of arrow shows the dependency in this sense 
    that destination node (variable) is dependent on source node.

@@

    The generative model is modified in a way that features of arguments (source and destination)
    will be generated from two new distributions, $T_1$ \& $T_2$ which are modeling entity types. The graphical model
    is shown in fig ???. This model not only clusters relations but also clusters entities to entity clusters.

@@

Yao et al. have evaluated their models in different settings. Their comparison against Mintz et al.?? previous work
 will be mentioned in the next chapter which is dedicated to distant supervision. They have used human judgments 
 to measure their models precision. Humans are asked to label 50 instances in each relation cluster and in order to measure
 the recall, induced relations are compared against Freebase. Table ?? shows the results.

@@

\chapter{Weakly Supervised on Relation Extraction Task}
\label{ch:related}

@@

The content of \cite{Huang2012} your proposal. Each topic occupies one section, each
with their own conclusion and future work.

>>>>

\usepackage{graphics}
\usepackage{epsfig}
\usepackage{times}
\usepackage{amsmath}
\usepackage{framed, color}
\usepackage{fancybox}
\usepackage{graphicx}
\definecolor{shadecolor}{rgb}{0.8,0.8,0.8}

@@

The aim of this paper is to review recent and influential methods on
Unsupervised Relation Extraction. In the first chapter, the definition and a general background
for relation extraction task is provided which identifies important aspects and
difficulties of the task. In the second chapter, four major previous works are
briefly reviewed. And
finally in the last chapter, the paper will be concluded by comparison of discussed methods and important lessons learned from each of them.

@@

\subsection{Inference Selectional Preferences}
\label{ch:improve}

@@

In order to model this type of constraint on discovery of paraphrases, Pantel et al. have proposed that
relations which are similar but are not sharing a same class of arguments should be filtered out. For each relation, 
they compute a distribution of possible semantic classes for its arguments. For two equivalent relations, they will be kept
if this distribution is similar for both.Yao et al. ??? also incorporate selectional preferences to their model and which we
will see in detailed in the last section.

Two models are proposed to compute this distribution. The first one, the distribution is computed jointly for both of arguments
and the second one two different distributions are computed for each argument. The computation is just a simple count.

The question that naturally arises is that how one can obtain these semantic classes? The answer is that
they are obtainable from lexical resources such as WordNet or they can be induced by clustering words.
The authors have used both methods. As the first approach, they have used top level nodes in WordNet and all their successors together
as semantic classes. They have also used CBC clustering algorithm ??? to induce semantic classes. 
In ??? brown and ??? Lin WU a similar approach but with different clustering algorithms has been chosen 
and the later is the current state-of-the-art method.

After computing selectional preferences for each relation, those relations which don't have similar selectional preference
distribution will be considered as inequivalent. The plausibility of an inference rule which contains two relations is
discussed in detailed in ??? %cite{LEDIR}.

Inducing word clusters and using independent selectional preferences distributions has been shown to outperform other models
and have the highest increase of accuracy compare to DIRT.

\subsection{Direction of Inference Rules}
\label{ch:improve}
So far all the similar relations are considered to be paraphrases nad they have bi-directional semantic equivallency relation.

Since this assumption doesn't hold for all the inference rules that are discovered by DIRT, Pantel et al. pushed their model
another step further to find the direction of implications among relations, in addition to just find equivalent relations.

They have used the results from DIRT and ISP to find out which direction holds for an implication over two relations.
having $relation_i \iff relation_j$ they want to examine if it holds or either of $relation_i \implies relation_j$
or $relation_j \implies relation_i$ is the correct rule.

the key assumption in ??? is that the direction is most likely from a specific relation to a more general relation.
By specific relation they mean a relation that has a narrow set of semantic classes and selectional preferences and 
a general relation is a relation with broader semantic classes. Number of acceptable semantic classes for each relation is a 
good measure for such purpose. If this number is greater for the antecedent then the direction is right otherwise it should be flipped.

In the next section we will review a method which operates in web-scale and extract relations with bootstraping.

@@

\textbf{Rel-LDA} is the first model proposed in (?? Yao). 
In this model, features, $f$, are generated from a distribution , $\Phi_{rf}$. Each type
 of relation is represented with a binary indicator variable, $r$. Each document is a mixture of few relations
  and relations are generated from a multinomial distribution $\Theta_{doc}$. $\Theta_{doc}$ is a distribution
  of relations for a specific document and can be shown as $P(r|doc)$. By choosing a right prior distribution for $\Theta$
   and $\Phi$ we can impose an assumption that any document contains a few number of relation types. 
   Another advantage of having prior is that it helps to avoid overfitting. Dirichlet prior with small parameter $\alpha$ is 
   chosen for this purpose in the paper. For more on the role of priors and specially Dirichlet prior
    please read ?? and ??.
    Rel-LDA is decribed with a graphical model 
     \begin{figure}[h!]
  \caption{Rel-LDA}
  \centering
    \includegraphics[width=0.5\textwidth]{rel-lda.eps}
    \label{fig:rel-lda}
\end{figure} in Figure ~\ref{fig:rel-lda} .

    Shaded circles are showing the observable variables and other circles are hidden variables except 
    the priors which are set by ourselves. The direction of arrow shows the dependency in this sense 
    that destination node (variable) is dependent on source node.

@@

    The generative model is modified in a way that features of arguments (source and destination)
    will be generated from two new distributions, $T_1$ \& $T_2$ which are modeling entity types. The graphical model
    is shown in
     \begin{figure}[h!]
  \caption{Type-LDA}
  \centering
    \includegraphics[width=0.5\textwidth]{type-lda.eps}
    \label{fig:type-lda}
\end{figure} 
Figure ~\ref{fig:type-lda} .
    This model not only clusters relations but also clusters entities to entity clusters.

@@

\iffalse Yao et al. have evaluated their models in different settings.  Their comparison against Mintz et al.?? previous work
 will be mentioned in the next chapter which is dedicated to distant supervision. \fi They have used human judgments 
 to measure their models precision. Humans are asked to label 50 instances in each relation cluster and in order to measure
 the recall, induced relations are compared against Freebase. Table ?? shows the results.

@@

\iffalse
\chapter{Weakly Supervised on Relation Extraction Task}
\label{ch:related}

@@

The content of \cite{Huang2012} your proposal. Each topic occupies one section, each
with their own conclusion and future work.
\fi
